---
title: "total baselines"
author: "Elizabeth Bose"
date: "12/4/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---
#import data
```{r setup, include=FALSE}
#import data
base1.0<-texture_baseline1
base2.0 <- texture_baseline2
base3.0 <- texture_baseline3
base4.0 <-texture_baseline4


#taking out outlier images that could not get accurate surface area thresholds due to bad lighting or irregular objects in them because accurate textural information will not be extractable from these images
base1.00 <- na.omit(base1.0)
base2.00<- na.omit(base2.0)
base3.00 <- na.omit(base3.0)
base4.00  <- na.omit(base4.0)

#name variables
base1 <- data.frame(path=base1.00$path, hour=base1.00$hour, coveredutof=base1.00$third_covered_UtoF, covered=base1.00$third_covered, baseline=base1.00$baseline, y=base1.00$y, asm=base1.00$Angular.Second.Moment, contrast=base1.00$Contrast, idm=base1.00$Inverse.Difference.Moment, corr=base1.00$Correlation, entropy=base1.00$Entropy, energy=base1.00$Energy, inertia=base1.00$Inertia, homogeneity=base1.00$Homogeneity, prominence=base1.00$Prominence, variance=base1.00$Variance, shade=base1.00$Shade, rq=base1.00$Rq, ra=base1.00$Ra, rsk=base1.00$Rsk, rku=base1.00$Rku, rv=base1.00$Rv, rp=base1.00$Rp, rc=base1.00$Rc, rt=base1.00$Rt, fpo=base1.00$FPO, mfov=base1.00$MFOV, fad=base1.00$FAD, mrv=base1.00$MRV, sa=base1.00$SA, area=base1.00$uncropped_sa)

base2 <- data.frame(path=base2.00$path, hour=base2.00$hour, coveredutof=base2.00$third_covered_UtoF, covered=base2.00$third_covered, baseline=base2.00$baseline, y=base2.00$y, asm=base2.00$Angular.Second.Moment, contrast=base2.00$Contrast, idm=base2.00$Inverse.Difference.Moment, corr=base2.00$Correlation, entropy=base2.00$Entropy, energy=base2.00$Energy, inertia=base2.00$Inertia, homogeneity=base2.00$Homogeneity, prominence=base2.00$Prominence, variance=base2.00$Variance, shade=base2.00$Shade, rq=base2.00$Rq, ra=base2.00$Ra, rsk=base2.00$Rsk, rku=base2.00$Rku, rv=base2.00$Rv, rp=base2.00$Rp, rc=base2.00$Rc, rt=base2.00$Rt, fpo=base2.00$FPO, mfov=base2.00$MFOV, fad=base2.00$FAD, mrv=base2.00$MRV, sa=base2.00$SA, area=base2.00$uncropped_sa)

base3 <- data.frame(path=base3.00$path, hour=base3.00$hour, coveredutof=base3.00$third_covered_UtoF, covered=base3.00$third_covered, baseline=base3.00$baseline, y=base3.00$y, asm=base3.00$Angular.Second.Moment, contrast=base3.00$Contrast, idm=base3.00$Inverse.Difference.Moment, corr=base3.00$Correlation, entropy=base3.00$Entropy, energy=base3.00$Energy, inertia=base3.00$Inertia, homogeneity=base3.00$Homogeneity, prominence=base3.00$Prominence, variance=base3.00$Variance, shade=base3.00$Shade, rq=base3.00$Rq, ra=base3.00$Ra, rsk=base3.00$Rsk, rku=base3.00$Rku, rv=base3.00$Rv, rp=base3.00$Rp, rc=base3.00$Rc, rt=base3.00$Rt, fpo=base3.00$FPO, mfov=base3.00$MFOV, fad=base3.00$FAD, mrv=base3.00$MRV, sa=base3.00$SA, area=base3.00$uncropped_sa)

base4 <- data.frame(path=base4.00$path, hour=base4.00$hour, coveredutof=base4.00$third_covered_UtoF, covered=base4.00$third_covered, baseline=base4.00$baseline, y=base4.00$y, asm=base4.00$Angular.Second.Moment, contrast=base4.00$Contrast, idm=base4.00$Inverse.Difference.Moment, corr=base4.00$Correlation, entropy=base4.00$Entropy, energy=base4.00$Energy, inertia=base4.00$Inertia, homogeneity=base4.00$Homogeneity, prominence=base4.00$Prominence, variance=base4.00$Variance, shade=base4.00$Shade, rq=base4.00$Rq, ra=base4.00$Ra, rsk=base4.00$Rsk, rku=base4.00$Rku, rv=base4.00$Rv, rp=base4.00$Rp, rc=base4.00$Rc, rt=base4.00$Rt, fpo=base4.00$FPO, mfov=base4.00$MFOV, fad=base4.00$FAD, mrv=base4.00$MRV, sa=base4.00$SA, area=base4.00$uncropped_sa)

```

#merge data into one
```{r}
base1.2 <-rbind(base1, base2)
base1.2.3 <-rbind(base1.2, base3)
base.all <- rbind(base1.2.3, base4)

#ordering distribution labels: T, F, A
base.all$coveredutof<-as.factor(base.all$coveredutof)
base.all$coveredutof<-factor(base.all$coveredutof, levels=rev(levels(base.all$coveredutof)))
print(levels(base.all$coveredutof)) #make sure order is T, F, A
#saving baseline # as factor instead of integer
str(base.all)
```
#summary stats
```{r}
#contingency table
library(sjPlot)
sjt.xtab(base.all$coveredutof,base.all$y,file="cont1.doc")
#summary statistics
library(table1)
library(boot)
base.all$coveredutof<-factor(base.all$coveredutof, levels=c("T", "F","A"),labels=c("Covered","Clumped","Gaps"))
label(base.all$coveredutof)<-"Distribution"
base.all$y<-factor(base.all$y,levels=c("FALSE","TRUE"),labels=c("FALSE","TRUE"))
label(base.all$y) <-"Image label"
label(base.all$asm)<-"Angular second moment"
label(base.all$shade)<-"Shade"
label(base.all$prominence)<-"Prominence"
label(base.all$rc)<-"Rc"
label(base.all$rsk)<-"Skewness"
label(base.all$mfov)<-"MFOV"
label(base.all$mrv)<-"MRV"
label(base.all$fad)<-"FAD"
label(base.all$area)<-"Area"
units(base.all$area)<-"%"
summary<-table1(~y+asm+shade+prominence+rsk+mfov+mrv+fad+area+coveredutof|baseline, data=base.all)
summary
```

#will want baseline 4 to be reference so need to reverse order of baselines
```{r}
base.all$baseline <- as.factor(base.all$baseline)
base.all$baseline <- factor(base.all$baseline, levels=rev(levels(base.all$baseline)))
```


#chi square test for independence to determine if variability in y label related to baseline number or distribution pattern
```{r}
#dependence of y label on distribution pattern
tbl= table(base.all$y, base.all$coveredutof)
tbl
chisq.test(tbl)
#dependence of y label on baseline number
tbl2= table(base.all$y, base.all$baseline)
tbl2
chisq.test(tbl2)
```


#excluding textural features based on multicolinearity to incorporate some into the model and standardizing
```{r}
#removing variables that are highly correlated
base.allb <- base.all[,c(2,3,5,6,7,15,17,20,24,27:29,31)]
base.allb$coveredutof<-factor(base.allb$coveredutof, levels=rev(levels(base.allb$coveredutof)))
print(levels(base.allb$coveredutof)) #want covered to be first so it is the reference
base.allb$baseline <- as.factor(base.allb$baseline)
base.allb$baseline <- factor(base.allb$baseline, levels=rev(levels(base.allb$baseline)))
print(levels(base.allb$baseline))#want 4 to be first so it is the reference

#standardizing
library(robustHD)
base.allb$zprominence <- standardize(base.allb$prominence)
base.allb$zasm <- standardize(base.allb$asm)
base.allb$zshade <- standardize(base.allb$shade)
base.allb$zrsk <- standardize(base.allb$rsk)
base.allb$zrc <- standardize(base.allb$rc)
base.allb$zmfov <- standardize(base.allb$mfov)
base.allb$zfad <- standardize(base.allb$fad)
base.allb$zmrv <- standardize(base.allb$mrv)
base.allb$zarea <- standardize(base.allb$area)
names(base.allb)

zbase.allb<- base.allb[,c(1:4,14:22)]#only standardized variables
base.allb <- base.allb[,c(1:13)]

```

#step function with textural features of interest with standardized independent variables
```{r}
zbase.allc <- zbase.allb
zbase.allc$coveredutof<-factor(zbase.allc$coveredutof, levels=rev(levels(zbase.allc$coveredutof)))
print(levels(zbase.allc$coveredutof)) #want covered to be first so it is the reference
zbase.allc$baseline <- factor(zbase.allc$baseline, levels=rev(levels(zbase.allc$baseline)))
print(levels(zbase.allc$baseline)) #make sure baseline 4 is the reference
str(zbase.allc)

modall. <- glm(y ~ ., family=binomial(link="logit"), data=zbase.allc)
summary(modall.) #all significant, continue with step function

fit <- glm(y~.,family=binomial(link="logit"), data=zbase.allc)
n= length(zbase.allb$y)
step<- stepAIC(fit, directions="forward", k=2)
step$anova

step.model2 <- glm(y ~ hour + coveredutof + baseline + zasm + zprominence + zshade + zrsk + zrc + zmfov + zfad + zmrv + zarea, family=binomial(link="logit"), data=zbase.allc)
#use vif to compute VIF, if above 5 or 10, then excessive multicolinearity
car::vif(step.model2)#no multicolinearity
summary(step.model2) #AIC is 28050

#wald test
library(car)
wald.sm2<-Anova(step.model2, test="Wald")
wald.sm2

exp(cbind(OR=coef(step.model2),confint(step.model2)))
(exp(cbind(OR=coef(step.model2),confint(step.model2)))-1)*100#this is the percent change in the odds for a one unit increase in the independent variables
(step.model2$null.deviance-step.model2$deviance)/step.model2$nul2.deviance

#mod.all.dist is model made at bottom
anova(modall.area.dist, step.model2, test="Chisq") #the added complexity of the model with texture features is significant

step.model2.0 <- glm(y ~ hour + coveredutof + zasm + zprominence + zshade + zrsk + zrc + zmfov + zfad + zmrv + zarea, family=binomial(link="logit"), data=zbase.allc)
anova(step.model2.0, step.model2, test="Chisq")#including baseline in model is significant

step.model2.00 <- glm(y ~ baseline + coveredutof + zasm + zprominence + zshade + zrsk + zrc + zmfov + zfad + zmrv + zarea, family=binomial(link="logit"), data=zbase.allc)
anova(step.model2.00, step.model2, test="Chisq") #adding time is not significant 

```

#diagnostic plots of model with texture features, these look really good except the residauls vs fitted values are a little unbalanced
```{r}
library(statmod)
qr.sm2 <-qresiduals(step.model2)
hist(qr.sm2, breaks=200)
qqnorm(qr.sm2)
abline(a=0, b=1)
plot(step.model2$fitted.values, qr.sm2)
abline(h=0,col=2,lty=2)
```

#plots of asm of each image plotted with T/F labeled
```{r}
library(ggplot2)
#jitterplot of all area values
asm.all<- ggplot(base.all, aes(x=hour,y=asm))+geom_jitter(aes(color=y), alpha=1/3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","brown3"))+xlab("Time (hours)")+ylab("Angular second moment")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "bottom")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

asm.1<- ggplot(base1, aes(x=hour,y=asm))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("Time (hours)")+ylab("Angular second moment")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = c(0.1,0.9))+ guides(colour = guide_legend(override.aes = list(size=6)))+ scale_x_continuous(breaks=seq(0,50,10))
asm.1

asm.2<- ggplot(base2, aes(x=hour,y=asm))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("Time (hours)")+ylab("Angular second moment")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = c(0.1,0.9))+ guides(colour = guide_legend(override.aes = list(size=6)))+ scale_x_continuous(breaks=seq(0,50,10))

asm.3<- ggplot(base3, aes(x=hour,y=asm))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("Time (hours)")+ylab("Angular second moment")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = c(0.1,0.9))+ guides(colour = guide_legend(override.aes = list(size=6)))+ scale_x_continuous(breaks=seq(0,50,10))

asm.4<- ggplot(base4, aes(x=hour,y=asm))+geom_jitter(aes(color=y), alpha=1/3, size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("Time (hours)")+ylab("Angular second moment")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = c(0.1,0.9))+ guides(colour = guide_legend(override.aes = list(size=6)))+ scale_x_continuous(breaks=seq(0,50,10))
```

#plots of prominence of each image plotted with T/F labeled
```{r}
#jitterplot of all area values
prominence.all<- ggplot(base.all, aes(x=hour,y=prominence))+geom_jitter(aes(color=y), alpha=1/3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","brown3"))+ggtitle("")+xlab("Time (hours)")+ylab("Prominence")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

prominence.1<- ggplot(base1, aes(x=hour,y=prominence))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Prominence")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))+ scale_y_continuous(breaks=seq(0,600000000,100000000))

prominence.2<- ggplot(base2, aes(x=hour,y=prominence))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Prominence")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

prominence.3<- ggplot(base3, aes(x=hour,y=prominence))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Prominence")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

prominence.4<- ggplot(base4, aes(x=hour,y=prominence))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Prominence")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))
```

#plots of shade of each image plotted with T/F labeled
```{r}
#jitterplot of all area values
shade.all<- ggplot(base.all, aes(x=hour,y=shade))+geom_jitter(aes(color=y), alpha=1/3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","brown3"))+xlab("Time (hours)")+ylab("Shade")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

shade.1<- ggplot(base1, aes(x=hour,y=shade))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Shade")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

shade.2<- ggplot(base2, aes(x=hour,y=shade))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Shade")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

shade.3<- ggplot(base3, aes(x=hour,y=shade))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Shade")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

shade.4<- ggplot(base4, aes(x=hour,y=shade))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Shade")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))
```

#plots of rsk of each image plotted with T/F labeled
```{r}
rsk.all<- ggplot(base.all, aes(x=hour,y=rsk))+geom_jitter(aes(color=y), alpha=1/3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","brown3"))+xlab("Time (hours)")+ylab("Rsk")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

rsk.1<- ggplot(base1, aes(x=hour,y=rsk))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Rsk")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

rsk.2<- ggplot(base2, aes(x=hour,y=rsk))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Rsk")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

rsk.3<- ggplot(base3, aes(x=hour,y=rsk))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Rsk")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

rsk.4<- ggplot(base4, aes(x=hour,y=rsk))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Rsk")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))
```

#plots of rc of each image plotted with T/F labeled
```{r}
#jitterplot of all area values
rc.all<- ggplot(base.all, aes(x=hour,y=rc))+geom_jitter(aes(color=y), alpha=1/3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","brown3"))+xlab("Time (hours)")+ylab("Rc")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

rc.1<- ggplot(base1, aes(x=hour,y=rc))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Rc (gray scale values)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

rc.2<- ggplot(base2, aes(x=hour,y=rc))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Rc (gray scale values)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

rc.3<- ggplot(base3, aes(x=hour,y=rc))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Rc (gray scale values)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

rc.4<- ggplot(base4, aes(x=hour,y=rc))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Rc (gray scale values)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))
```

#plots of mfov of each image plotted with T/F labeled
```{r}
#jitterplot of all area values
mfov.all<- ggplot(base.all, aes(x=hour,y=mfov))+geom_jitter(aes(color=y), alpha=1/3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","brown3"))+xlab("Time (hours)")+ylab("MFOV")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))
    

mfov.1<- ggplot(base1, aes(x=hour,y=mfov))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("MFOV (degrees)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))


mfov.2<- ggplot(base2, aes(x=hour,y=mfov))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("MFOV (degrees)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

mfov.3<- ggplot(base3, aes(x=hour,y=mfov))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("Time")+ylab("MFOV (degrees)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

mfov.4<- ggplot(base4, aes(x=hour,y=mfov))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("MFOV (degrees)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))
```

#plots of fad of each image plotted with T/F labeled
```{r}
#jitterplot of all area values
fad.all<- ggplot(base.all, aes(x=hour,y=fad))+geom_jitter(aes(color=y), alpha=1/3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+xlab("Time (hours)")+ylab("FAD")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))


fad.1<- ggplot(base1, aes(x=hour,y=fad))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("FAD (degrees)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

fad.2<- ggplot(base2, aes(x=hour,y=fad))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("FAD (degrees)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

fad.3<- ggplot(base3, aes(x=hour,y=fad))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("FAD (degrees)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

fad.4<- ggplot(base4, aes(x=hour,y=fad))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("FAD (degrees)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

```

#plots of mrv of each image plotted with T/F labeled
```{r}
#jitterplot of all area values
mrv.all<- ggplot(base.all, aes(x=hour,y=mrv))+geom_jitter(aes(color=y), alpha=1/3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+xlab("")+ylab("MRV")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

mrv.1<- ggplot(base1, aes(x=hour,y=mrv))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("MRV")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

mrv.2<- ggplot(base2, aes(x=hour,y=mrv))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("MRV")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

mrv.3<- ggplot(base3, aes(x=hour,y=mrv))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("MRV")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

mrv.4<- ggplot(base4, aes(x=hour,y=mrv))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("MRV")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))
```

#plots of area of each image plotted with T/F labeled
```{r}
#jitterplot of all area values
area.all<- ggplot(base.all, aes(x=hour,y=area))+geom_jitter(aes(color=y), alpha=1/3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","brown3"))+xlab("Time (hours)")+ylab("Area covered (%)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

area.1<- ggplot(base1, aes(x=hour,y=area))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Area covered (%)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

area.2<- ggplot(base2, aes(x=hour,y=area))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Area covered (%)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

area.3<- ggplot(base3, aes(x=hour,y=area))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Area covered (%)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))

area.4<- ggplot(base4, aes(x=hour,y=area))+geom_jitter(aes(color=y), alpha=1/3,size=3)+ theme_bw() + theme(
  panel.border = element_blank(), 
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(), 
  axis.line = element_line(colour = "black"))+scale_color_manual(breaks=c("TRUE","FALSE"), values=c("darkgrey","red2"))+ggtitle("")+xlab("")+ylab("Area covered (%)")+theme(
    plot.title=element_text(hjust=0.5),
    axis.text=element_text(size=20),
    axis.title = element_text(size=24),
    title =element_text(size=26),
    legend.text=element_text(size=20),
    legend.title= element_blank(),
    legend.position = "none")+ guides(colour = guide_legend(override.aes = list(size=5)))+ scale_x_continuous(breaks=seq(0,50,10))
```